---
title: "Demo wheat"
author: "Khagendra"
date: "June 12, 2017"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}

Demo<-read.csv(file='Wheat yield_Demo.csv')
Demoselect<-Demo[,19:28]
summary(Demoselect)
```

# Mean,SD, SE and CI ['g' grainwt/ m2]

# Mean: Treatment and districtwise 
```{r }
library(ggplot2)
library(Rmisc)
subDatase <- summarySE(Demo, measurevar="Grainwt", groupvars=c("Treat","District"));subDatase
```
# Mean: Treatment, district and VDCwise
```{r}
subDatasevdc <- summarySE(Demo, measurevar="Grainwt", groupvars=c("Treat","District",'VDC'));subDatasevdc
```
# Mean: District and wheat varietywise 
```{r cars}
subDatasevar <- summarySE(Demo, measurevar="Grainwt", groupvars=c("District","wheat.variety"));subDatasevar
```

# Model fitting
```{r}
library(nlme)
fit1<-lme(Grainwt~Treat+wheat.variety, random=~1|District/VDC/Farmer,data=Demo,method='REML')
anova(fit1)
```

# Normality and homogenity of varience test
```{r}
par(mfrow=c(2,2))
plot(residuals(fit1)~fitted(fit1),data=Demoselect)
hist(residuals(fit1))# check the homogenity of varience
qqnorm(residuals(fit1)) # check normality
qqline(residuals(fit1))
shapiro.test(residuals(fit1,type='response'))
```


#Pairwise comparision of treatment
```{r}
library(lsmeans)
lsd<-lsmeans(fit1,pairwise~wheat.variety);lsd
cld(lsd, Letters='abcd')
```

## Districtwise selection of data and means
#Banke
```{r}
Ban<-Demoselect[Demo$District=='Banke',]
Banke <- summarySE(Ban, measurevar="Grainwt", groupvars=c("Treat"));Banke
```
#Bardia
```{r}
Bar<-Demoselect[Demo$District=='Bardiya',]
Bardia <- summarySE(Bar, measurevar="Grainwt", groupvars=c("Treat"));Bardia
```
#Kailali
```{r}
Kai<-Demoselect[Demo$District=='Kailali',]
Kailali <- summarySE(Kai, measurevar="Grainwt", groupvars=c("Treat"));Kailali
```
#kanchanpur
```{r}
Kanch<-Demoselect[Demo$District=='Kanchanpur',]
Kanchanpur<-summarySE(Kanch,measurevar = 'Grainwt',groupvars = c('Treat')); Kanchanpur
```
## Boxplot: Yield by districts 
```{r}
library(ggplot2)
Plotall<-ggplot(Demo, aes(District,Grainwt))+
  geom_boxplot()+labs(title=" ", x="Districts", y = "Wheat yield (g/m2)");Plotall

## re-scaling Y axis
Plotall+scale_y_continuous(breaks=c(0,200, 400, 600, 800),labels = c(0,2,4,6,8))+
  labs(title=" ", x="Districts", y = "Wheat yield (Mg/ha)")
```

#Boxplot: Yield by Variety
```{r}
library(ggplot2)
ggplot(Demo, aes(x=wheat.variety, y=Grainwt))+
  geom_boxplot((aes(color=Treat)))+labs(title=" ", x="Variety", y = "Wheat yield (Mg/ha)")+
  scale_y_continuous(breaks=c(0,200, 400, 600, 800),labels = c(0,2, 4, 6,8))
```

# Boxplot: Yield by districts along with treatments
```{r}
ggplot(Demo, aes(x=District, y=Grainwt))+
  geom_boxplot(aes(color=Treat))+
  labs(title=" ", x="Districts", y = "Wheat yield (g/m2)")+
  scale_y_continuous(breaks=c(0,200, 400, 600, 800),labels = c(0,2, 4, 6,8))+
  labs(title=" ", x="Districts", y = "Wheat yield (Mg/ha)")
```
  

#Yield by variety along with treatments
```{r }
ggplot(Demo, aes(x=wheat.variety, y=Grainwt))+
  geom_boxplot((aes(color=Treat)))+labs(title=" ", x="Variety", y = "Wheat yield (g/m2)")
```

# Yield distribution by treatment and VDCwise in Banke district
```{r}
Banke<-ggplot(Ban, aes(x=VDC, y=Grainwt))+
  geom_boxplot(aes(color=Treat))+
   labs(title=" ", x="Banke", y = "Wheat yield (g/m2)", label=".")+
  theme(axis.text=element_text(size=rel(1)))+
  
  theme(axis.title.y = element_text(size = rel(1.2), angle = 90));Banke

# re-scaling Y axis
Banke+scale_y_continuous(breaks=c(0,200, 400, 600, 800),labels = c(0,2, 4, 6,8))+
  labs(title=" ", x="Banke", y = "Wheat yield (Mg/ha)")
```

# Yield distribution by treatment and VDC in Bardia district
```{r}
Bardia<-ggplot(Bar, aes(x=VDC, y=Grainwt))+
  geom_boxplot(aes(color=Treat))+
  labs(title=" ", x="Bardia", y = "Wheat yield (g/m2)", label=".")
  #stat_summary(fun.y = "mean", geom = "text", label=".", size= 20, color= "blue");Bardia
 #geom_jitter(width = 0.2, aes(colour = factor(Treat))

# re-scaling Y axis
Bardia+scale_y_continuous(breaks=c(0,200, 400, 600, 800),labels = c(0,2, 4, 6,8))+
  labs(title=" ", x="Bardia", y = "Wheat yield (Mg/ha)")
```

#Kailali district
```{r}
Kailali<-ggplot(Kai, aes(x=VDC, y=Grainwt))+
  geom_boxplot(aes(color=Treat))+
  labs(title=" ", x="Kailali", y = "Wheat yield (g/m2)", label=".")

Kailali+scale_y_continuous(breaks=c(0,200, 400, 600, 800),labels = c(0,2, 4, 6,8))+
  labs(title=" ", x="Kailali", y = "Wheat yield (Mg/ha)")
```
#Kanchanpur district
```{r}
Kanchanpur<-ggplot(Kanch, aes(x=VDC, y=Grainwt))+
  geom_boxplot(aes(color=Treat))+
  labs(title=" ", x="Kanchanpur", y = "Wheat yield (g/m2)", label=".")

Kanchanpur+scale_y_continuous(breaks=c(0,200, 400, 600, 800),labels = c(0,2, 4, 6,8))+
  labs(title=" ", x="Kanchanpur", y = "Wheat yield (Mg/ha)")
  
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


